---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# worldcupR

<!-- badges: start -->
<!-- badges: end -->

The top 8 teams in the world cup are relatively well-known by pundits, but a lot of uncertainty remains as to who will finally lift the trophy. The goal of worldcupR is to simulate a World Cup knockout tournament based on historical match data from previous world cups by focusing on teams' historical scoring strength to predict the outcomes of the upcoming World Cup.

## Installation

You can install the development version of worldcupR like so:

``` r
devtools::install_github("Svenbeck-maastricht/worldcupR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(worldcupR)
library(dplyr)
library(doParallel)
## basic example code
teams <- c("Brazil", "Germany", "France", "Netherlands", "Argentina", "Spain", "England", "Portugal")
#historical statistic for a team
team_summary("Brazil")
#simulate a tournament
simulate_tournament(teams)$champion
#run simulations (500) either sequentially or parallel
winners_seq <- tournament_seq(teams)
winners_par <- tournament_par(teams)
table(winners_seq)
table(winners_par)

bench1 <- microbenchmark::microbenchmark(
  tournament_par(teams),
  tournament_seq(teams),
  times =5
)

#plot the sequential winner probability table
plot_win_probability(winners_seq)

```

# Full Analysis

For a complete example including parallel simulation, benchmarking, and win probability plots, see 'worldcup_analysis.R' in the project root

#Plot team history

```{r pressure, echo = FALSE}
plot_team_history("Brazil")
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
