---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# worldcupR

<!-- badges: start -->
<!-- badges: end -->

The top 8 teams in the world cup are relatively well-known to pundits, but a lot of uncertainty remains as to who will finally lift the trophy. The goal of worldcupR is to simulate a World Cup knockout tournament based on historical match data from previous world cups by focusing on teams' historical scoring strength to predict the outcomes of the upcoming World Cup. Simulations are run sequentially and in parallel across 500 runs. Functions to explore and plot a team's historical record and for the final win probability simulated across the 500 runs are made available. Users of the package can switch the teams they would like to simulate in the knockout stages.

## Installation

You can install the development version of worldcupR like so:

``` r
devtools::install_github("Svenbeck-maastricht/worldcupR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(worldcupR)
library(dplyr)
library(doParallel)
## basic example code
teams <- c("Brazil", "Germany", "France", "Netherlands", "Argentina", "Spain", "England", "Portugal")
#historical statistic for a team
team_summary("Brazil")
#simulate a tournament
simulate_tournament(teams)$champion
#run simulations (500) either sequentially or parallel
winners_seq <- tournament_seq(teams)
winners_par <- tournament_par(teams)
table(winners_seq)
table(winners_par)

bench1 <- microbenchmark::microbenchmark(
  tournament_par(teams),
  tournament_seq(teams),
  times =5
)

#plot the sequential winner probability table
plot_win_probability(winners_seq)

```

# Full Analysis

For a complete example including parallel simulation, benchmarking, and win probability plots, see 'worldcup_analysis.R' in the project root

#Plot team history

```{r pressure, echo = FALSE}
plot_team_history("Brazil")
```

#Functions

`simulate_match()`: simulates a single match based on historical scoring strength
`simulate_tournament()`: simulates a single knockout tournament
`tournament_seq()`: runs 500 simulations sequentially
`tournament_par()`: runs 500 simulations in parallel
`team_summary()`: returns historical World Cup stats for a team
`plot_team_history()`: plots a team's match history
`plot_win_probability()`: plots bar chart of win probabilities in the sequential MC simulation
